The Minimal Retroreflective Microfacet Model

### 2025-06-26 article.tex
Tweak listing

\noindent\begin{minipage}[tb]{\linewidth}
\begin{lstlisting}[
    language=GLSL,
    caption=Pseudo code to implement the retro-reflective microfacet model.,
    label=lst:implementation,
    nolol=true,
    frame=trBL
    ]
vec3 retroGGX(vec3 L, vec3 V, vec3 N, vec3 X, vec3 Y)
{
    vec3 Vp = -reflect(V,N); // jp - is this wrong? Why the minus sign
    float NdotL = dot(N, L);
    float NdotV = dot(N, Vp);
    if (NdotL < 0 || NdotV < 0) return vec3(0);

@@

    float val = Ks * D * G * F / (4 * NdotL * NdotV);
    return vec3(val);
}
\end{lstlisting}
\end{minipage}

>>>>

\noindent\begin{minipage}[tb]{\linewidth}
\begin{lstlisting}[
    language=GLSL,
    caption=Pseudo code to implement the retro-reflective microfacet model.,
    label=lst:implementation,
    nolol=true,
    frame=trBL
    ]
vec3 brdf_retro(vec3 L, vec3 V, vec3 N, vec3 X, vec3 Y)
{
    vec3 Vp = -reflect(V,N); // jp - is this wrong? Why the minus sign

    // The following could all be replaced with:
    // We could give the simplified form of brdf_ggx, but not essential.
    return brdf_ggx(L, Vp, N, X, Y);

    /*
    float NdotL = dot(N, L);
    float NdotV = dot(N, Vp);
    if (NdotL < 0 || NdotV < 0) return vec3(0);

@@

    float val = Ks * D * G * F / (4 * NdotL * NdotV);
    return vec3(val);
    */
}
\end{lstlisting}
\end{minipage}
